\section{Definition of parameters for control files}
\label{section:def_control}

\subsection{Block {\tt view\_transform\_ctl}}
\label{href_t:view_transform_ctl}
Parameters to construct view transform matrix and projection matrix are defined in this block. \\
(Back to Section \ref{sec:viewmatrix_menu}) \\

\subsubsection{Block {\tt image\_size\_ctl}}
\label{href_t:image_size_ctl}
Number of pixels of the image is defined in this block.

\paragraph{\tt x\_pixel\_ctl}
\label{href_t:x_pixel_ctl}
\verb|[NUM_PIXEL_X]| \\
Number of pixels in the horizontal direction \verb|[NUM_PIXEL_X]| is defined by integer.

\paragraph{\tt y\_pixel\_ctl}
\label{href_t:y_pixel_ctl}
\verb|[NUM_PIXEL_Y]| \\
Number of pixels in the veritcal direction \verb|[NUM_PIXEL_Y]| is defined by integer.

\subsubsection{Array {\tt viewpoint\_in\_viewer\_ctl [DIRECTION] [POSITION]}}
\label{href_t:viewpoint_in_viewer_ctl}
Position of eye in the viewer coordinate is defined in each \verb|[DIRECTION]| and \verb|[POSITION]|. \verb|[DIRECTION]| is set by text (\verb|x, y,| or \verb|z|), and \verb|[POSITION]| is set by real.

\subsubsection{Array {\tt look\_at\_point\_ctl [DIRECTION] [POSITION]}}
\label{href_t:look_at_point_ctl}
Position to look at is defined in each \verb|[DIRECTION]| and \verb|[POSITION]|. \verb|[DIRECTION]| is set by text (\verb|x, y,| or \verb|z|), and \verb|[POSITION]| is set by real.

\subsubsection{\tt scale\_factor\_ctl  [SCALE]}
\label{href_t:scale_factor_ctl}
Scale of the object is defined by real. In viewer coordinate, object is scaled by 1 / \verb|[SCALE]| times.

\subsubsection{Array {\tt view\_rotation\_vec\_ctl [DIRECTION] [POSITION]}}
\label{href_t:view_rotation_vec_ctl}
Direction of the rotation axis of the object is defined by \verb|[DIRECTION]| and \verb|[POSITION]|. \verb|[DIRECTION]| is set by text (\verb|x, y,| or \verb|z|), and \verb|[POSITION]| is set by real.

\subsubsection{\tt view\_rotation\_deg\_ctl  [DEGREE]}
\label{href_t:view_rotation_deg_ctl}
Angle of the rotation of the object is defined by \verb|[DEGREE]|.

\subsubsection{Block {\tt projection\_matrix\_ctl}}
\label{href_t:projection_matrix_ctl}
Parameters of projection is defined in this block.

\paragraph{\tt perspective\_angle\_ctl}
\label{href_t:perspective_angle_ctl}
\verb|[PERSPECTIVE]| \\
Angle of perspective \verb|[PERSPECTIVE]| is defined by real.

\paragraph{\tt perspective\_xy\_ratio\_ctl}
\label{href_t:perspective_xy_ratio_ctl}
\verb|[XY_RATIO]| \\
Aspect ratio of horizontal and vertical screen \verb|[XY_RATIO]| is defined by real.

\paragraph{\tt perspective\_near\_ctl}
\label{href_t:perspective_near_ctl}
\verb|[NEAR]| \\
Nearrest distance from eye \verb|[NEAR]| is defined by real.

\paragraph{\tt perspective\_far\_ctl}
\label{href_t:perspective_far_ctl}
\verb|[FAR]| \\
Farest distance from eye \verb|[FAR]| is defined by real.


\subsubsection{Block {\tt streo\_view\_parameter\_ctl}}
\label{href_t:streo_view_parameter_ctl}
Parameters of streo image is defined in this block. This block is only used for the streo view.

\paragraph{\tt focal\_point\_ctl}
\label{href_t:focal_point_ctl}
\verb|[FOCAL]| \\
Focal point \verb|[FOCAL]| is defined by real.

\paragraph{\tt eye\_separation\_ctl}
\label{href_t:eye_separation_ctl}
\verb|[SEPARATION]| \\
Eye separation \verb|[SEPARATION]| is defined by real.



\subsection{Block {\tt pvr\_color\_ctl}}
\label{href_t:pvr_color_ctl}
Parameters to construct colormap and colorbar information in this block. \\
(Back to Section \ref{sec:viewmatrix_menu}) \\

\subsubsection{Block {\tt colormap\_ctl}}
\label{href_t:colormap_ctl}
Parameters to construct colormap information in this block. \\

\paragraph{\tt colormap\_mode\_ctl}
\label{href_t:colormap_mode_ctl}
\verb|[COLORMAP_MODE]| \\
Colormap \verb|[COLORMAP_MODE]| is defined by character. The following colormap is applicable:
\begin{description}
\item{{\tt rainbow}: } Rainbow color map.
\item{{\tt blue\_to\_red}: } Change color from brue to red.
\item{{\tt grayscale}: } Grayscale.
\item{{\tt symmetric\_grayscale}: } Grayscale with respect to amplitude of data.
\end{description}


\paragraph{\tt data\_mapping\_ctl}
\label{href_t:data_mapping_ctl}
\verb|[COLORMAPPING_TYPE]| \\
Color mapping interpolation mode \verb|[COLORMAPPING_TYPE]| is defined by the following:
\begin{description}
\item{{\tt minmax}: } Linear scaling between \hyperref[href_t:range_min_ctl]{\tt range\_min\_ctl} and \hyperref[href_t:range_max_ctl]{\tt range\_max\_ctl}.
\item{{\tt colormap\_list}: } Linearly chanded color scale between feature points. the feature points of the data \verb|[DATA]| and color salec at this value \verb|[COLOR_SCALE]| are defined \\ 
in \hyperref[href_t:linear_opacity_ctl]{\tt color\_table\_ctl}.
\end{description}

\paragraph{Array {\tt color\_table\_ctl}}
\label{href_t:color_table_ctl}
\verb|[DATA]    [COLOR_SCALE]| \\
List of the feature points of the data \verb|[DATA]| and color scale at this value \verb|[COLOR_SCALE]| are defined by real. \verb|[COLOR_SCALE]| is set between 0. and 1.0. The color between the feature points are interpolated by the linear function.

\paragraph{\tt opacity\_style\_ctl}
\label{href_t:opacity_style_ctl}
\verb|[OPACITY_MODE]| \\
Opacity mode \verb|[OPACITY_MODE]| is defined by the following:
\begin{description}
\item{{\tt constant}: } Constant opacity defined by \hyperref[href_t:constant_opacity_ctl]{\tt constant\_opacity\_ctl}
\item{{\tt point\_linear}: } Linearly chanded opacity between feature points. the feature points of the data \verb|[DATA]| and opacity at this value \verb|[OPACITY]| are defined \\ 
in \hyperref[href_t:linear_opacity_ctl]{\tt linear\_opacity\_ctl}.
\end{description}

\paragraph{\tt constant\_opacity\_ctl}
\label{href_t:constant_opacity_ctl}
\verb|[OPACITY]| \\
Constant opacity \verb|[OPACITY]| is defined by real.

\paragraph{Array {\tt linear\_opacity\_ctl}}
\label{href_t:linear_opacity_ctl}
\verb|[DATA]    [OPACITY]| \\
List of the feature points of the data \verb|[DATA]| and opacity at this value \verb|[OPACITY]| are defined by real. The opacity between the feature points are interpolated by the linear function.

\paragraph{\tt range\_min\_ctl}
\label{href_t:range_min_ctl}
\verb|[MIN_VALUE]| \\
Minimum value of the color and opacity map \verb|[MIN_VALUE]| is defined by real.

\paragraph{\tt range\_max\_ctl}
\label{href_t:range_max_ctl}
\verb|[MAX_VALUE]| \\
Maximum value of the color and opacity map \verb|[MAX_VALUE]| is defined by real.



\subsubsection{Block {\tt colorbar\_ctl}}
\label{href_t:colorbar_ctl}
Parameters to construct colorbar information in this block. \\

\paragraph{\tt colorbar\_switch\_ctl}
\label{href_t:colorbar_switch_ctl}
\verb|[SWITCH]| \\
Switch to display colorbar. \verb|[SWITCH]| is set to be \verb|On| or \verb|Off|.

\paragraph{\tt colorbar\_scale\_ctl}
\label{href_t:colorbar_scale_ctl}
\verb|[SWITCH]| \\
Switch to display numbers in colorbar. \verb|[SWITCH]| is set to be \verb|On| or \verb|Off|. This switch is always "\verb|On|" in CalypsoView.

\paragraph{\tt font\_size\_ctl}
\label{href_t:font_size_ctl}
\verb|[SIZE]| \\
Size of text of the color bar \verb|[SIZE]| is defined by integer. This value is not used in CalypsoView.

\paragraph{\tt num\_grid\_ctl}
\label{href_t:num_grid_ctl}
\verb|[NUM_OF_GRID]| \\
Number of grids in color bar \verb|[NUM_OF_GRID]| is defined by integer. This value is not used in CalypsoView.

\paragraph{\tt iflag\_zeromarker}
\label{href_t:iflag_zeromarker}
\verb|[SWITCH]| \\
Switch to display position of zero in colorbar. \verb|[SWITCH]| is set to be \verb|On| or \verb|Off|. This switch is always "\verb|On|" in CalypsoView.

\paragraph{\tt colorbar\_range}
\label{href_t:colorbar_range}
\verb|[MIN_VALUE]  [MAX_VALUE] | \\
Range of the color bar is defined here. \verb|[MIN_VALUE]| and \verb|[MAX_VALUE]| are defined by real. This switch does not reflect from reading from the file because the range of the color bar is defined by the values in \hyperref[href_t:range_min_ctl]{\tt range\_min\_ctl} and \hyperref[href_t:range_max_ctl]{\tt range\_max\_ctl}.


\paragraph{\tt axis\_label\_switch}
\label{href_t:axis_label_switch}
\verb|[SWITCH]| \\
Switch to display axis. \verb|[SWITCH]| is set to be \verb|On| or \verb|Off|. This switch does not reflect from reading from the file.



